Multisequence algorithm for coarse-grained biomolecular simulations: exploring the sequence-structure relationship of proteins

### 2017-06-07 Supplement.tex
final changes

\usepackage[left=3cm, right=2.5cm, top=2.5cm, bottom=3cm]{geometry}
%\usepackage{graphicx}% Include figure files
\usepackage[export]{adjustbox}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth,center]{meanE}
\caption{ Comparison of the average energy, $\left < E\right >$, as calculated at 8 different temperatures by the ST and MS algorithms for the 4 model sequences (A) A1, (B) N1, (C) R1, and (D) R2. Statistical 1$\sigma$ errors, estimated from 32 independent runs for each method (see Table~II), are shown but are smaller than the plot symbols for all points.}
\end{figure}

>>>>

\usepackage[left=3cm, right=2.5cm, top=2.5cm, bottom=3cm]{geometry}
%\usepackage{graphicx}% Include figure files
\usepackage[export]{adjustbox}
\usepackage{caption}

\renewcommand{\figurename}{FIG.~S}

@@

\begin{figure}[h]
\includegraphics[width=0.8\textwidth,center]{meanE}
\caption*{FIG.~S1. Comparison of the average energy, $\left < E\right >$, as calculated at 8 different temperatures by the ST and MS algorithms for the 4 model sequences (A) A1, (B) N1, (C) R1, and (D) R2. Statistical 1$\sigma$ errors, estimated from 32 independent runs for each method (see Table~II), are shown but are smaller than the plot symbols for all points.}
\end{figure}
